STA610 Case Study 1 Team 4 Report

### 2021-03-21 Draft Report 3.21.Rmd
new version

#model with no random slope is better
#best model!!!
mod_final <- lmer(data=df_filter, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + source, REML=F)
BIC(mod_final)
#8412.338

@@

## Results
#### Fixed Effects
```{r, message=FALSE}
#knitr::kable(fixef(mod1))
#confint(mod1)[3:11,]

# extract coefficients
coefs <- data.frame(coef(summary(mod_final)))
# use normal distribution to approximate p-value
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
knitr::kable(coefs, col.names = c("Estimate", "Std.Error", "t-value", "P-value"))
```

#### need to change numbers after finalizing model
* dose_per_mg: Controlling for other variables, for every one milligram increase of dosage, the price per mg of oxymorphone increases by a multiplicative effect of exp(-0.01524395) = 0.9848717, about a 1.51% reduction.

* bulk_purchase: “Not bulk purchase” is the reference group.
  * Controlling for other variables, bulk purchase reduces the price per mg of oxymorphone by a multiplicative effect of exp(-0.17013501) = 0.8435509, about a 15.64% reduction.

* source: “Source: Unknown” is the reference group. 
  * Controlling for other variables, purchasing oxymorphone with Internet source tends to increase the price per mg by a multiplicative effect of exp(0.12686001) = 1.135258, about a 13.53% increase than the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with Internet Pharmacy source tends to reduce the price per mg by a multiplicative effect of exp(-0.44349281) = 0.6417908, about a 35.82% reduction of the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with personal source tends to increase the price per mg by a multiplicative effect of exp(0.06140303) = 1.063327, about a 6.33% increase than the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with “heard it” source tends to increase the price per mg by a multiplicative effect of exp(0.18025958) = 1.197528, about a 19.75% increase than the price per mg of oxymorphone for people with unknown drug source.

#### Random Effects
```{r}
#VarCorr(mod1)
Variance <- c(0.0233, 0.5028)
Std.Dev <- c(0.1526, 0.7091)
Groups <- c("state (Intercept)", "Residual")

REvar <- cbind(Groups, Variance, Std.Dev)

knitr::kable(REvar, col.names = c("Group", "Variance", "Std.Dev"))
```
The within-state variance $\sigma^2$ is 0.5028, which is much larger than the across-state variance $\tau^2$, 0.0233.

@@

```{r}
ICC <- 0.047
knitr::kable(ICC, col.names = "Intraclass Correlation")
```
Intraclass correlation is 0.047, which means values are not very similar from the same state.

>>>>

#model with no random slope is better
#best model!!!
mod_final <- lmer(data=df_filter, log_ppm ~ (1 | state) + dose_per_mg + bulk_purchase + source + Primary_Reason, REML=F)
BIC(mod_final)
#8412.338

@@

## Start here

## Results
#### Fixed Effects
```{r, message=FALSE}
#knitr::kable(fixef(mod1))
#confint(mod1)[3:11,]
# extract coefficients
coefs <- data.frame(coef(summary(mod_final)))
# use normal distribution to approximate p-value
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
knitr::kable(coefs, col.names = c("Estimate", "Std.Error", "t-value", "P-value"))
```

* dose_per_mg: Controlling for other variables, for every one milligram increase of dosage, the price per mg of oxymorphone increases by a multiplicative effect of exp(-0.0151868) = 0.9849279, about a 1.51% reduction.

* bulk_purchase: “Not bulk purchase” is the reference group.
  * Controlling for other variables, bulk purchase reduces the price per mg of oxymorphone by a multiplicative effect of exp(-0.1691121) = 0.8444142, about a 15.56% reduction.

* source: “Source: Unknown” is the reference group. 
  * Controlling for other variables, purchasing oxymorphone with Internet source tends to increase the price per mg by a multiplicative effect of exp(0.1339468) = 1.143332, about a 14.33% increase than the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with Internet Pharmacy source tends to reduce the price per mg by a multiplicative effect of exp(-0.4584378) = 0.6322706, about a 36.77% reduction than the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with personal source tends to increase the price per mg by a multiplicative effect of exp(0.0565153) = 1.058143, about a 5.81% increase than the price per mg of oxymorphone for people with unknown drug source.
  * Controlling for other variables, purchasing oxymorphone with “heard it” source tends to increase the price per mg by a multiplicative effect of exp(0.1790027) = 1.196024, about a 19.6% increase than the price per mg of oxymorphone for people with unknown drug source.

* Primary Reason: “Primary_Reason: Blank” is the reference group. 
  * Controlling for other variables, purchasing oxymorphone with primary reason Left unanswered tends to increase the price per mg by a multiplicative effect of exp(0.0176846) = 1.017842, about a 1.78% increase than the price per mg of oxymorphone for people with Blank primary reason.
  * Controlling for other variables, purchasing oxymorphone with primary reason Other or unknown tends to increase the price per mg by a multiplicative effect of exp(0.0486307) = 1.049833, about a 4.98% increase than the price per mg of oxymorphone for people with Blank primary reason.
  * Controlling for other variables, purchasing oxymorphone with primary reason Self-treat tends to increase the price per mg by a multiplicative effect of exp(0.1034974) = 1.109043, about a 10.9% increase than the price per mg of oxymorphone for people with Blank primary reason.
  * Controlling for other variables, purchasing oxymorphone with primary reason Enjoyment tends to increase the price per mg by a multiplicative effect of exp(0.1838890) = 1.201882, about a 20.19% increase than the price per mg of oxymorphone for people with Blank primary reason.
  * Controlling for other variables, purchasing oxymorphone with primary reason Resell tends to reduce the price per mg by a multiplicative effect of exp(-0.3179197) = 0.7276612, about a 27.23% reduction than the price per mg of oxymorphone for people with Blank primary reason.
  * Controlling for other variables, purchasing oxymorphone with primary reason Refuse to answer tends to increase the price per mg by a multiplicative effect of exp(0.0564516) = 1.058075, about a 5.81% increase than the price per mg of oxymorphone for people with Blank primary reason.

#### Random Effects
```{r}
#VarCorr(mod_final)
Variance <- c(0.02292, 0.50060)
Std.Dev <- c(0.15140 , 0.70753)
Groups <- c("state (Intercept)", "Residual")
REvar <- cbind(Groups, Variance, Std.Dev)
knitr::kable(REvar, col.names = c("Group", "Variance", "Std.Dev"))
```
The within-state variance $\sigma^2$ is 0.5006, which is much larger than the across-state variance $\tau^2$, 0.02292.

@@

```{r}
ICC <- 0.044
knitr::kable(ICC, col.names = "Intraclass Correlation")
```
Intraclass correlation is 0.044, which means values are not very similar from the same state.
